19Q2

### 2020-01-07 19Q2.Rmd

```{r load_drug_rds}
# ccle_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds")
# ctrp_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ctrp_all_edited.rds")
# gdsc_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_gdsc_all_edited.rds")

@@

```{r, eval = TRUE}
crispr_fus <- readRDS("./data_munging/19Q2/crispr_fusions.rds")
# crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes.rds")
crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes_20200103.rds")
```

```{r, eval = FALSE}
crispr_allgenes <- readRDS("./../htscreens_giant_files/crispr_data_19Q2_allgenes.rds")
crispr_fus_allgenes <- readRDS("./../htscreens_giant_files/crispr_fusions_allgenes.rds")
crispr_prot_allgenes <- readRDS("./../htscreens_giant_files/crispr_protein_changes_allgenes.rds")
```

@@

```{r ccl_venn, eval=FALSE}
ccle_ccls <- unique(ccle$DepMap_ID)
ctrp_ccls <- unique(ctrp$DepMap_ID)
gdsc_ccls <- unique(gdsc$DepMap_ID)
crispr_ccls <- unique(crispr$DepMap_ID)

@@

```{r drug_venn, eval=FALSE}
ccle_drugs <- unique(ccle$Drug)
ctrp_drugs <- unique(ctrp$Drug)
gdsc_drugs <- unique(gdsc$Drug)

@@

```{r}
dataframe = crispr_prot
grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change")
g2p_list = unique(as.character(g2p_prot$Gene_Protein_Change[!is.na(g2p_prot$Gene_Protein_Change)]))
outfile = "./data_munging/rds/crispr_signif_protein_changes.rds"

@@

# ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 20, height = 10, units = "in")
```

@@

# FIGURES

@@

```{r fig.height=8, fig.width=15, eval=FALSE}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
ht_mut_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
ht_mut_grob <- grid.grabExpr(draw(ht_mut_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))

@@

ccle_mut_filt <- filter(ccle, Drug_Gene %in% filter(ccle_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
ccle_mut_filt_plot <- ggplot(data = ccle_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  facet_wrap(~ Drug_Gene, ncol = 5) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
  labs(title = "CCLE", x = "Mutation Status", y = "AUC") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

ctrp_mut_filt <- filter(ctrp, Drug_Gene %in% filter(ctrp_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
ctrp_mut_filt_plot <- ggplot(data = ctrp_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  facet_wrap(~ Drug_Gene, ncol = 7) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07,) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
  labs(title = "CTRP", x = "Mutation Status", y = "AUC") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

@@

```{r prot_changes, eval = FALSE, fig.height=15, fig.width=15}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.012)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.135)
ht_prot_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
ht_prot_grob <- grid.grabExpr(draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))

@@

## CN/GE

```{r CN_GE, eval = FALSE, fig.height=10, fig.width=15}
# Copy number

@@

ctrp_cn_cor_filt <- filter(ctrp_cn_cor, CN_p < 0.05)
ctrp_cn_filt <- filter(ctrp, Drug_Gene %in% ctrp_cn_cor_filt$Drug_Gene)
ctrp_text <- data.frame(label = paste0("r = ", round(ctrp_cn_cor_filt$CN_r, digits = 3), ",\n", ctrp_cn_cor_filt$p.format), Drug_Gene = ctrp_cn_cor_filt$Drug_Gene)
ctrp_cn_filt_plot <- ggplot(data = ctrp_cn_filt, aes(x = CN, y = Score) )+
  facet_wrap(~ Drug_Gene) +
  geom_point(fill = "steelblue4", pch = 21, size = 1, alpha = 0.7) +
  geom_text(data = ctrp_text,
            mapping = aes(x = +Inf, y = +Inf, label = label,
            hjust = 1.1, vjust = 1.2)) +
  labs(title = "CTRP", x = "Copy number (log2)", y = "AUC") +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

gdsc_cn_cor_filt <- filter(gdsc_cn_cor, CN_p < 0.05)

@@

gs_cn_ge <- gList(arrangeGrob(ht_cn_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(crispr_cn_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ccle_cn_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ctrp_cn_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ht_ge_grob, left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(crispr_ge_filt_plot), left = textGrob("F", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ccle_ge_filt_plot), left = textGrob("G", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ctrp_ge_filt_plot), left = textGrob("H", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(gdsc_ge_filt_plot), left = textGrob("I", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))

@@

## First draft figures

>>>>

```{r load_drug_rds, eval=FALSE}
# ccle_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds")
# ctrp_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ctrp_all_edited.rds")
# gdsc_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_gdsc_all_edited.rds")

@@

```{r, eval=TRUE}
crispr_fus <- readRDS("./data_munging/19Q2/crispr_fusions.rds")
# crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes.rds")
crispr_prot <- readRDS("./../htscreens_giant_files/crispr_protein_changes_20200103.rds")
```

```{r, eval=FALSE}
crispr_allgenes <- readRDS("./../htscreens_giant_files/crispr_data_19Q2_allgenes.rds")
crispr_fus_allgenes <- readRDS("./../htscreens_giant_files/crispr_fusions_allgenes.rds")
crispr_prot_allgenes <- readRDS("./../htscreens_giant_files/crispr_protein_changes_allgenes.rds")
```

## Filter duplicate rows

```{r, eval=FALSE}
# All nrow = 0
# crispr_prot_dup <- crispr_prot[duplicated(crispr_prot),]
# ccle_prot_dup <- ccle_prot[duplicated(ccle_prot),]
# ctrp_prot_dup <- ctrp_prot[duplicated(ctrp_prot),]
# gdsc_prot_dup <- gdsc_prot[duplicated(gdsc_prot),]

crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2.rds") %>% drop_na(Gene)
crispr$Gene_Lin <- with(crispr, paste0(Gene, "_", disease))
crispr_unique <- unique(crispr)
saveRDS(crispr_unique, file = "./data_munging/19Q2/crispr_data_19Q2_unique.rds", compress = "xz")

ccle_unique <- unique(ccle)
saveRDS(ccle_unique, file = "./data_munging/19Q2/ccle_data_19Q2_unique.rds", compress = "xz")
gdsc_unique <- unique(gdsc)
saveRDS(gdsc_unique, file = "./data_munging/19Q2/gdsc_data_19Q2_unique.rds", compress = "xz")
ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs)
ctrp_unique <- unique(ctrp_filt)
saveRDS(ctrp_unique, file = "./data_munging/19Q2/ctrp_data_19Q2_g2pdrugs_unique.rds", compress = "xz")
```

```{r}
crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2_unique.rds")
ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2_unique.rds")
ctrp <- readRDS("./data_munging/19Q2/gdsc_data_19Q2_unique.rds")
gdsc <- readRDS("./data_munging/19Q2/ctrp_data_19Q2_g2pdrugs_unique.rds")
```

@@

```{r ccl_venn, eval=FALSE}
ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2.rds") %>% drop_na(Drug)
ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q2.rds") %>% drop_na(Drug)
gdsc <- readRDS("./data_munging/19Q2/gdsc_data_19Q2.rds") %>% drop_na(Drug)
crispr <- readRDS("./data_munging/19Q2/crispr_data_19Q2.rds") %>% drop_na(Gene)

ccle_ccls <- unique(ccle$DepMap_ID)
ctrp_ccls <- unique(ctrp$DepMap_ID)
gdsc_ccls <- unique(gdsc$DepMap_ID)
crispr_ccls <- unique(crispr$DepMap_ID)

@@

```{r drug_venn, eval=FALSE}
ccle <- readRDS("./data_munging/19Q2/ccle_data_19Q2.rds") %>% drop_na(Drug)
ctrp <- readRDS("./../htscreens_giant_files/ctrp_data_19Q2.rds") %>% drop_na(Drug)
gdsc <- readRDS("./data_munging/19Q2/gdsc_data_19Q2.rds") %>% drop_na(Drug)

@@

```{r, eval=FALSE}
dataframe = crispr_prot
grouping = c("Gene_Protein_Change", "Drug", "Drug_Gene_Protein_Change")
g2p_list = unique(as.character(g2p_prot$Gene_Protein_Change[!is.na(g2p_prot$Gene_Protein_Change)]))
outfile = "./data_munging/rds/crispr_signif_protein_changes.rds"

@@

ggsave("./plots/manuscript/crispr_spearman_corr_plot.png", crispr_spearman_corr_plot, device = "png", dpi = 450, width = 20, height = 10, units = "in")
```

@@

# MANUSCRIPT

@@

## Mutation status figure

```{r}
crispr_g2p_count <- filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
ccle_g2p_count <- filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
ctrp_g2p_count <- filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
gdsc_g2p_count <- filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
```

```{r mut_status_fig, fig.height=8, fig.width=15, eval=FALSE}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
ht_mut_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
ht_mut_grob <- grid.grabExpr(draw(ht_mut_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))

@@

ccle_mut_filt <- filter(ccle, Drug_Gene %in% filter(ccle_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
ccle_mut_filt_plot <- ggplot(data = ccle_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  facet_wrap(~ Drug_Gene, ncol = 5) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "springgreen4", "0" = "palegreen3")) +
  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
  coord_cartesian(ylim = c(0, 1.10)) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
  labs(title = "CCLE", x = "Mutation Status", y = "AUC") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "mintcream", colour = "mintcream", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

ctrp_mut_filt <- filter(ctrp, Drug_Gene %in% filter(ctrp_signif_g2p_dg_summ, p < 0.05)$Drug_Gene)
ctrp_mut_filt_plot <- ggplot(data = ctrp_mut_filt, mapping = aes(x = as.character(Mutation), y = Score)) +
  facet_wrap(~ Drug_Gene, ncol = 7) +
  geom_violin(aes(fill = as.character(Mutation))) +
  geom_boxplot(outlier.shape = NA, width = 0.07,) +
  scale_x_discrete(labels = c("0" = "Wildtype", "1" = "Mutant")) +
  scale_fill_manual(name = "Mutation Status", labels = c("Wildtype", "Mutant"), values = c("1" = "steelblue4", "0" = "slategray3")) +
  scale_y_continuous(breaks = seq(0, 1.00, by = 0.25), labels = c("0.00", "0.25", "0.50", "0.75", "1.00")) +
  coord_cartesian(ylim = c(0, 1.10)) +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35, label.y = 1.1) +
  labs(title = "CTRP", x = "Mutation Status", y = "AUC") +
  theme(legend.position = "none", axis.title.x = element_blank(),
        panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

@@

## Protein changes figure

```{r}
test2 <- select(g2p_prot, Direction_Curated, Gene,Gene_Protein_Change) %>% drop_na(Direction_Curated) %>% unique()
unique(test2$Gene)

crispr_g2p_prot<- filter(crispr_signif_prot, Gene_Protein_Change %in% unique(g2p_prot$Gene_Protein_Change), InG2P == "Yes")
ccle_g2p_prot <- filter(ccle_signif_prot, Drug_Gene_Protein_Change %in% unique(g2p_prot$Drug_Gene_Protein_Change), InG2P == "Yes")
sum(!is.na(ccle_g2p_prot$p))
ctrp_g2p_prot <- filter(ctrp_signif_prot, Drug_Gene_Protein_Change %in% unique(g2p_prot$Drug_Gene_Protein_Change), InG2P == "Yes")
sum(!is.na(ctrp_g2p_prot$p))
gdsc_g2p_prot <- filter(gdsc_signif_prot, Drug_Gene_Protein_Change %in% unique(g2p_prot$Drug_Gene_Protein_Change), InG2P == "Yes")
sum(!is.na(gdsc_g2p_prot$p))
```

```{r prot_changes_fig, eval=FALSE, fig.height=15, fig.width=15}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.012)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.135)
ht_prot_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
ht_prot_grob <- grid.grabExpr(draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))

@@

## CN/GE figure

```{r CN_GE_fig, eval=FALSE, fig.height=10, fig.width=15}
# Copy number

@@

ctrp_cn_cor_filt <- filter(ctrp_cn_cor, CN_p < 0.05)
ctrp_cn_filt <- filter(ctrp, Drug_Gene %in% ctrp_cn_cor_filt$Drug_Gene)
# ctrp_text <- data.frame(label = paste0("r = ", round(ctrp_cn_cor_filt$CN_r, digits = 3), ",\n", ctrp_cn_cor_filt$p.format), Drug_Gene = ctrp_cn_cor_filt$Drug_Gene)
# ctrp_cn_filt_plot <- ggplot(data = ctrp_cn_filt, aes(x = CN, y = Score) )+
#   facet_wrap(~ Drug_Gene) +
#   geom_point(fill = "steelblue4", pch = 21, size = 1, alpha = 0.7) +
#   geom_text(data = ctrp_text,
#             mapping = aes(x = +Inf, y = +Inf, label = label,
#             hjust = 1.1, vjust = 1.2)) +
#   labs(title = "CTRP", x = "Copy number (log2)", y = "AUC") +
#   theme(legend.position = "none",
#         panel.background = element_rect(fill = "whitesmoke", colour = "whitesmoke", size = 0.5, linetype = "solid"),
#         panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
#         panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

gdsc_cn_cor_filt <- filter(gdsc_cn_cor, CN_p < 0.05)
gdsc_cn_filt <- filter(gdsc, Drug_Gene %in% gdsc_cn_cor_filt$Drug_Gene)
gdsc_text <- data.frame(label = paste0("r = ", round(gdsc_cn_cor_filt$CN_r, digits = 3), ",\n", gdsc_cn_cor_filt$p.format), Drug_Gene = gdsc_cn_cor_filt$Drug_Gene)
gdsc_cn_filt_plot <- ggplot(data = gdsc_cn_filt, aes(x = CN, y = Score) )+
  facet_wrap(~ Drug_Gene) +
  geom_point(fill = "turquoise4", pch = 21, size = 1, alpha = 0.7) +
  geom_text(data = gdsc_text,
            mapping = aes(x = +Inf, y = +Inf, label = label,
            hjust = 1.1, vjust = 1.2)) +
  labs(title = "GDSC", x = "Copy number (log2)", y = "AUC") +
  theme(legend.position = "none",
        panel.background = element_rect(fill = "lightcyan", colour = "lightcyan", size = 0.5, linetype = "solid"),
        panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"),
        panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"))

@@

gs_cn_ge <- gList(arrangeGrob(ht_cn_grob, left = textGrob("A", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(crispr_cn_filt_plot), left = textGrob("B", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ccle_cn_filt_plot), left = textGrob("C", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(gdsc_cn_filt_plot), left = textGrob("D", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ht_ge_grob, left = textGrob("E", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(crispr_ge_filt_plot), left = textGrob("F", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ccle_ge_filt_plot), left = textGrob("G", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(ctrp_ge_filt_plot), left = textGrob("H", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))),
             arrangeGrob(ggplotGrob(gdsc_ge_filt_plot), left = textGrob("I", x = unit(1, "npc"), y = unit(.97, "npc"), gp = gpar(fontsize = 20, fontface = "bold"))))

@@

Fusions are completely driven by HL lineage: HL cell lines are the only cell lines that contain ABL1-BCR, BCR-ABL1, and PML-PARA fusions.
```{r}
test <- unique(select(fus, disease, FusionPair, Fusion_Status)) %>% filter(Fusion_Status == "Yes")
test
```

## Lineages

Mutation:
```{r}
crispr_mut_lin <- filter(crispr_signif_lin, InG2P == "Yes")
ccle_mut_lin <- filter(ccle_signif_dgl, InG2P == "Yes")
ctrp_mut_lin <- filter(ctrp_signif_dgl, InG2P == "Yes")
gdsc_mut_lin <- filter(gdsc_signif_dgl, InG2P == "Yes")
```

```{r}
crispr_test <- filter(crispr, Gene_Lin == "PTCH1_skin")
ggplot(crispr_test, aes(x = as.character(Mutation), y = Score)) +
  geom_boxplot() +
  geom_point() +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35)
```

## OLD: First draft figures
